### 2019-06-25 cv/cv-body.tex
Update CV

@@

Fisheries.

@@

\begin{description}
\tightlist
\item[2018]
\textbf{Anderson, S.C.}, E.A. Keppel, and A.M. Edwards. A reproducible
data synopsis for over 100 species of British Columbia groundfish.
Canadian Science Advisory Secretariat (CSAS) Research Document. Accepted
at regional peer-review meeting November 2018.
\item[2018]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018.
\end{description}

>>>>

Freshwater, C., \textbf{S.C. Anderson}, K.R. Holt, A.-M. Huang, C.A.
Holt. Weakened portfolio effects constrain management effectiveness for
population aggregates. In press at Ecological Applications.
Ward, E.J., \textbf{S.C. Anderson}, L.A. Damiano, M.E. Hunsicker,
M.A.\ Litzow. Modeling regimes with extremes: the `bayesdfa' package for
identifying and forecasting common trends and anomalies in multivariate
time-series data. In press at The R Journal.

@@

Fisheries. \url{https://doi.org/10.1111/faf.12364}.

@@

\begin{description}
\tightlist
\item[2018]
\textbf{Anderson, S.C.}, E.A. Keppel, and A.M. Edwards. A reproducible
data synopsis for over 100 species of British Columbia groundfish.
Canadian Science Advisory Secretariat (CSAS) Research Document 2019/041.
In press.
\item[2018]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018.
\end{description}
